Towards a Planckian standard kilogram

### 2018-04-07 other-formats/aa/ms.tex
rsos format

\title{Towards a Planckian standard kilogram}
\subtitle{}

@@

\abstract
% context heading (optional)
% {} leave it empty if necessary  
{As the kilogram assumes its new definition in terms of $h,c,$ and the
  standard second, it is interesting to think about a possible future
  definition entirely in terms of fundamental constants.  A kilogram
  defined as an integer multiple of the Planck mass (or
  4594xxxx$\times\sqrt{\hbar c/G}$) would cause no significant change
  from its current value.}
% aims heading (mandatory)
{The practical hurdle to this Planckian kilogram is measuring $G$
  three or four orders of magnitude better than currently known, so as
  to find the unknown digits xxxx.  We study a possible scenario for
  doing so with an artificial two-body orbit.}
% methods heading (mandatory)
{The cleanest (admittedly, not the cheapest) option is to place the
  system on a Trojan orbit to minimize external gravitational
  perturbations, and enclose it in a cavity chilled to liquid-helium
  temperatures, to suppress radiation pressure.}
% results heading (mandatory)
{Data analysis would involve marginalizing over at least 15~nuisance
  parameters (6~for orbital parameters and 9~for fictitious forces)
  but that, we show, is feasible.}
% conclusions heading (optional), leave it empty if necessary 
{}

>>>>

\title{Towards a Planckian standard kilogram}
\subtitle{A scenario for measuring $G$ using an artificial two-body orbit}

@@

\abstract
% context heading (optional)
% {} leave it empty if necessary  
{As the kilogram assumes its new definition in terms of $h,c,$ and the
  standard second, it is interesting to think about a possible future
  definition entirely in terms of fundamental constants.
  A kilogram could, in principle, be defined as an integer multiple of
  the Planck mass (or 4594????$\times\sqrt{\hbar c/G}$) without
  significantly altering its current value.  The practical hurdle is
  measuring $G$ four orders of magnitude better than currently known,
  in order to fix the four unknown digits.}
% aims heading (mandatory)
{We assess the prospects for measuring $G$ to the desired accuracy
  using an artificial two-body orbit.}
% methods heading (mandatory)
{The cleanest (admittedly, not the cheapest) option is to place the
  system on a Trojan orbit to minimize external gravitational
  perturbations, and enclose it in a cavity chilled to liquid-helium
  temperatures, to suppress radiation pressure.}
% results heading (mandatory)
{Data analysis would involve marginalizing over at least 15~nuisance
  parameters (6~for orbital parameters and 9~for fictitious forces)
  but that, we show, is feasible.}
% conclusions heading (optional), leave it empty if necessary 
{A more complicated system in Earth orbit should be taken seriously.}
